RNA-seq from 4 cell populations

### 2021-07-28 deconvolution/fans4/molec_profiling.Rmd
fix dependency

cd /hpc/users/hoffmg01/work/cmc_analysis/src
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

```{r load.packages, echo=FALSE, message=FALSE, results='hide', cache=FALSE}
suppressPackageStartupMessages({
library(variancePartition)
library(limma)
library(edgeR)
library(mvIC)
library(reshape2)
library(qvalue)
library(data.table)
library(BiocParallel)
library(knitr)
library(org.Hs.eg.db)
library(kableExtra)
library(ggplot2)
library(cowplot)
library(scran)
library(SummarizedExperiment)
library(gridExtra)
library(openxlsx)
library(synapser)
library(githubr)
synLogin()
library(EnsDb.Hsapiens.v86)
detach("package:EnsDb.Hsapiens.v86", unload=TRUE)
library(EnsDb.Hsapiens.v86)
ensdb = EnsDb.Hsapiens.v86
})

@@

```{r predict.celltype}
library(nnet)
library(PRROC)

>>>>

# cd /hpc/users/hoffmg01/work/cmc_analysis/src
cd /hpc/users/hoffmg01/work/CMC/covarr-de/deconvolution/fans4
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

```{r load.packages, echo=FALSE, message=FALSE, results='hide', cache=FALSE}
suppressPackageStartupMessages({
library(variancePartition)
library(limma)
library(edgeR)
library(mvIC)
library(reshape2)
library(qvalue)
library(data.table)
library(BiocParallel)
library(knitr)
library(org.Hs.eg.db)
library(kableExtra)
library(ggplot2)
library(cowplot)
library(scran)
library(SummarizedExperiment)
library(gridExtra)
library(openxlsx)
library(synapser)
library(nnet)
library(PRROC)
library(githubr)
synLogin()
library(EnsDb.Hsapiens.v86)
detach("package:EnsDb.Hsapiens.v86", unload=TRUE)
library(EnsDb.Hsapiens.v86)
})

@@

```{r predict.celltype}
df_class = lapply(1:10, function(k){
